Detecting threats of violence in YouTube comments

### 2016-02-17 submission.tex
Baseline results

\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the data
set has been manually split into sentences as part of the annotation
process.  We performed tokenization, lemmatization, PoS-tagging and
dependency parsing using the SpaCy
toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard
Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more
coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
dependency parser assigns an analysis in compliance with the ClearNLP
converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example
dependency graph from the data set. The data set was further enriched
with the cluster labels described in Turian et
al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering
algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
corpus containing Reuters English newswire text, with approximately 63
million words and 3.3 million sentences. We vary the number of clusters to be either 100,
320, 1000 or 3200 clusters and use the full cluster label.
 WordNet REF

\begin{figure*}
\begin{dependency}[arc edge, text only label, theme=simple]
  \begin{deptext}[column sep=.2cm]
    i \& m \& fucking \& scared \& kill \& them \& d \& : \\
   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
  \end{deptext}
  \depedge{2}{1}{\large nsubj}
  \depedge{2}{8}{\large punct}
  \depedge{2}{4}{\large acomp}
  \depedge{4}{3}{\large amod}
  \depedge{2}{5}{\large conj}
  \depedge{5}{6}{\large dobj}
  \depedge{5}{7}{\large advmod}
  \deproot[edge unit distance=1.5ex]{2}{}
\end{dependency}
\caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
\label{fig:dep}
\end{figure*}

\paragraph{Classifiers}

\paragraph{Tuning}

\paragraph{Features}
Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
\begin{description}
\setlength\itemsep{0em}
\item[Lexical] word form, lemma
\item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
\item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
\end{description}
These features are structured according to a set of \emph{feature
  templates}, which introduce varying degrees of linear order and
syntactic context: bag-of-features (unordered), bigrams, trigrams and
dependency triples. These feature templates are applied to the feature
types presented above, in order to yield features like the following
for our examples sentence in Figure \ref{fig:dep}:

@@

\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
\end{itemize}
Our lexical features are very specific and require the exact
combination of two lexical items in order to apply to a new instance.
Following \newcite{Jos:Pen:2009}, we therefore experiment with
generalization of features by backoff to a more general category,
e.g. from word form to lemma or PoS. A dependency triple over word
forms like $<$kill, dobj, them$>$ would thus be generalized to
$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
trigram and dependency triple features.
\subsection{Results}

@@

\subsection{Held-out results}M

>>>>

\paragraph{Pre-processing}Since threat annotation is performed on the sentence level, the data
set has been manually split into sentences as part of the annotation
process.  We performed tokenization, lemmatization, PoS-tagging and
dependency parsing using the SpaCy
toolkit\footnote{https://spacy.io/}.  SpaCy assigns both the standard
Penn Treebank PoS-tags \cite{Mar:San:Mar:93}, as well as the more
coarse-grained Universal PoS tag set of \newcite{Pet:Das:McD:12}. The
dependency parser assigns an analysis in compliance with the ClearNLP
converter \cite{Cho:Pal:12}, see Figure \ref{fig:dep} for an example
dependency graph from the data set. The data set was further enriched
with the cluster labels described in Turian et
al.~\shortcite{Tur:Rat:Ben:10}, created using the Brown clustering
algorithm \cite{Bro:deS:Mer:92} and induced from the RCV1 corpus, a
corpus containing Reuters English newswire text, with approximately 63
million words and 3.3 million sentences. We vary the number of
clusters to be either 100, 320, 1000 or 3200 clusters and use the full
cluster label.  We also make use of the WordNet resource
\cite{wordnet} to determine a word's synset, parent and grandparent
synset.

\begin{figure*}
\begin{center}
\begin{dependency}[arc edge, text only label, theme=simple]
  \begin{deptext}[column sep=.2cm]
    i \& m \& fucking \& scared \& kill \& them \& d \& : \\
   \tag{\smaller pron} \& \tag{\smaller verb} \& \tag{\smaller verb} \& \tag{\smaller adj} \& \tag{\smaller verb} \& \tag{\smaller pron} \& \tag{\smaller x} \& \tag{\smaller punct} \\
  \end{deptext}
  \depedge{2}{1}{\large nsubj}
  \depedge{2}{8}{\large punct}
  \depedge{2}{4}{\large acomp}
  \depedge{4}{3}{\large amod}
  \depedge{2}{5}{\large conj}
  \depedge{5}{6}{\large dobj}
  \depedge{5}{7}{\large advmod}
  \deproot[edge unit distance=1.5ex]{2}{}
\end{dependency}
\caption{Dependency parse of example sentence from the data set, with assigned uPOS tags.}
\label{fig:dep}
\end{center}
\end{figure*}

\paragraph{Classifiers}
Toolkits and references
\paragraph{Tuning}
Short on tuning
\paragraph{Features}
Based on the enriched data set, as described above, we experiment with the following lexical, morphosyntactic and semantic feature types:
\begin{description}
\setlength\itemsep{0em}
\item[Lexical] word form, lemma
\item[Morphosyntactic] Penn Treebank (PTB) or Universal (uPOS) PoS and Dependency Relation
\item[Semantic] Brown cluster label (100, 320, 1000 and 3200 clusters) and WordNet synset, parent synset and grandparent synset
\end{description}
These features are structured according to a set of \emph{feature
  templates}, which introduce varying degrees of linear order and
syntactic context: bag-of-features (unordered), bigrams, trigrams and
dependency triples. These feature templates are applied to the feature
types presented above, in order to yield features like the following
for our examples sentence in Figure \ref{fig:dep}:

@@

\item \{$<$m, nsubj, i$>$, $<$root, root, m$>$, $<$scared, amod, fucking$>$, $<$m, acomp, scared$>$, $<$m, conj, kill$>$, $<$kill, dobj, them$>$, $<$kill, advmod, d$>$, $<$m, punct, :$>$ \}
\end{itemize}
Our lexical features are very specific and require the exact
combination of two lexical items in order to apply to a new instance.
Following \newcite{Jos:Pen:2009}, we therefore experiment with
generalization of features by backoff to a more general category,
e.g. from word form to lemma or PoS. A dependency triple over word
forms like $<$kill, dobj, them$>$ would thus be generalized to
$<$VERB, dobj, them$>$ using \emph{head-backoff} and $<$kill, dobj,
PRON$>$ using \emph{modifier-backoff}. We apply backoff to bigram,
trigram and dependency triple features.
\subsection{Development results}
Table \ref{tab:baseline} shows baseline results in terms of F-score
for bag-of, bigram and trigram templates over lexical features (word
form and lemma). The presented results constitute the best F-scores
after tuning (which was only done on the MaxEnt classifier and the
SVM, not on the random forest classifier), as discussed above. The
overall best result came from the logistic regression classifier with
the bag of word form feature set. Generally we see that feature sets
containing bag of lexical features in some form outperform the
$n$-gram feature sets.
The feature set we will use as a baseline in the next stage of our
experiments is bag of word forms. The feature set recieved an F-score
of $0.6123$, with a precision of $0.6777$ and a recall of $0.5585$,
using the MaxEnt classifier after tuning. We will also be
using only the MaxEnt classifier for the remainder of the
feature set experiments.
\begin{table*}
  \begin{center}
    \begin{tabular}{lrrr}
      \toprule

      & MaxEnt & SVM & Random Forest \\
      \midrule
      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $0.3582$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
      Bag of lemmas & $0.5902$ & $0.5982$ & $0.3483$ \\
      Bigrams & $0.4856$ & $0.4887$ & $\textbf{0.4683}$ \\
      Trigrams & $0.2776$ & $0.2856$ & $0.2673$ \\

      \bottomrule
      % Data fra firstPass i classify
      % Source/printFirstPassResults.py
    \end{tabular}
  \end{center}
  \caption{Results for baseline system; F-score for bag-of, bigram and trigram templates over lexical features (word form and lemma).}
  \label{tab:baseline}
\end{table*}

Morphosyntactic features:
- bag of, bigram, trigram of pos, deprel
- combine with baseline

Semantic features:
- bag of, bigram, trigram of Brown, WordNet
- combine with baseline

Combination of best from baseline, morphosyntactic and semantic

@@

\subsection{Held-out results}
